---
title: "JLo_Course9_Week3_HW"
author: "Joyce Lo"
date: "March 14, 2018"
output:
  ioslides_presentation: default
  beamer_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(suppressWarnings(suppressMessages(library("plotly", quietly=T))))
```

## Analysis on Wine and Spirits
- In the next few slides, we will analyze wines and spirits sold at BC Liquor Stores
- Specifically, we shall examine if there is any correlation between:
    + Alcohol Content and Class of Liquor


## Download and Format Data
- I am commenting some commands out because you only need it run once

```{r downloaddata, results='hide'}
#fileURL <- "http://pub.data.gov.bc.ca/datasets/176284/BC_Liquor_Store_Product_Price_List.csv"
#if(!file.exists("data")){dir.create("data")}
#download.file(fileURL, destfile = "./data/liquor.csv")
liquor <- read.csv("./data/liquor.csv")

#Remove rows with NA
liquor2 <- na.omit(liquor)


```

- Next, I will create a box plot that shows Alcohol Content by Liquor Class
- The graph is interactive so you can filter by Country of Origin of the liquor!


## Plot Alcohol Content by Liquor Class

```{r boxplot, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
q <- list(
  title = ""
)
p <- liquor2 %>%
  plot_ly(
    type='box',
    y = ~PRODUCT_ALCOHOL_PERCENT,
    x = ~PRODUCT_CLASS_NAME,
    color = ~PRODUCT_CLASS_NAME,
    text = ~PRODUCT_COUNTRY_ORIGIN_NAME,
    hoverinfo = 'text',
    mode = 'markers',
    transforms = list(
      list(
        type = 'filter',
        target = ~PRODUCT_COUNTRY_ORIGIN_NAME,
        operation = '=',
        value = unique(liquor2$PRODUCT_COUNTRY_ORIGIN_NAME)[1]
      )
    )) %>% layout(
        xaxis = q,
        updatemenus = list(
        list(
          type = 'dropdown',
          active = 0,
          buttons = list(
            list(method = 'restyle',
                 args=list('transforms[0].value', unique(liquor2$PRODUCT_COUNTRY_ORIGIN_NAME)[1]),
                 label = unique(liquor2$PRODUCT_COUNTRY_ORIGIN_NAME)[1]),
            list(method = 'restyle',
                 args=list('transforms[0].value', unique(liquor2$PRODUCT_COUNTRY_ORIGIN_NAME)[2]),
                 label = unique(liquor2$PRODUCT_COUNTRY_ORIGIN_NAME)[2]),
            list(method = 'restyle',
                 args=list('transforms[0].value', unique(liquor2$PRODUCT_COUNTRY_ORIGIN_NAME)[3]),
                 label = unique(liquor2$PRODUCT_COUNTRY_ORIGIN_NAME)[3])
          )
        )
      )
    )     
  
p
#plot_ly(liquor2, y= ~PRODUCT_ALCOHOL_PERCENT, color = ~PRODUCT_CLASS_NAME, type='box')
```

## End of Presentation
- Thank you!
